The Ranked Nearest Neighbour Interchange space

### 2019-06-10 paper.tex
conj: max dist(T,R) <=> alg computes R given T

\begin{conjecture}
    Algorithm~\ref{alg:max_dist_tree} computes a tree with maximum distance $\Delta(\rnniu)$ from a given tree $T$.
\end{conjecture}

According to Algorithm~\ref{alg:max_dist_tree}, the number of trees with maximum distance to a given tree $T$ depends on the number of cherries of $T$.
For caterpillar trees it is $(n-1)!$.

>>>>

\begin{conjecture}
    Let $T_1$ and $T_2$ be trees on $n$ taxa.
    It is $d(T_1,T_2) = \Delta(\rnniu)$ if, and only if, $T_2$ can be produced from $T_1$ by applying Algorithm~\ref{alg:max_dist_tree}.
\end{conjecture}

According to Algorithm~\ref{alg:max_dist_tree}, the number of trees with maximum distance to a given tree $T$ depends on the number of cherries of $T$ and the ranks of their internal nodes.
For caterpillar trees it is $(n-1)!$.
